---
title: "Describe Sensors and Entities"
author: "Neil Kester"
date: "4/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

# Purpose  

This function's purpose is to provide the user with four tibbles as a named list. The first tibble, named `SensorDescription`, lists all sensors present in the query, their sensor type, and set magnification. The second tibble, named `EntityIdToName` maps each machine readable entity ID to its corresponding human readable name. The third tibble, named `SensorToEntityId`, maps each sensor ID to the entity it is mounted to. This means each entity may be shown multiple times while each sensor only shows up once.  

The function uses the `modSim::mongoUnnest` function to query and un-nest the returned data until it is in a useable form. 

# mapSensorsAndEntities Function   


```{r}
#' Map Sensors and Entities
#'
#' This function accepts the same inputs as the `modSim::mongoUnnest` function
#'  minus the `unnestCols` parameter. It executes the requested query which is
#'  expected to be from the `AcquireModel.state.sensors` collection.  
#'
#' @param mongoUri This is a double quoted character string of the connection 
#'  object required for the simulation's MongoDB.  
#' @param mongoDb This is a double quoted character string of the database name 
#'  containing the required files.
#' @param mongoCollection This is a double quoted character string of the mongo
#'  collection within the named database containing the required information.
#' @param mongoQuery This is a double quoted character string containing the json
#'  query to pass to the MongoDB. Note that users should escape nested double
#'  quotes with the \ escape character.  
#' @param mongoFields This is a double quoted json object of collection fields
#'  that should be returned (annoted with `true`) and those that should not be
#'  returned (annoted with `false`). 
#'
#' @return This function returns a four element named list of tibbles that 
#'  describe all sensors and entities, their IDs and description.  
#'
#' @importFrom modSim mongoUnnest
#' @importFrom dplyr distinct
#' 
#' @export mapSensorsAndEntities
mapSensorsAndEntities <- function(mongoUri,
                                  mongoDb,
                                  mongoCollection,
                                  mongoFields,
                                  mongoQuery){

    sensorState <- modSim::mongoUnnest(mongoUri = mongoUri,
                                                        mongoDb = mongoDb,
                                                        mongoCollection = mongoCollection,
                                                        mongoFields = mongoFields,
                                                        mongoQuery = mongoQuery,
                                                        unnestCols = "state")
    
    sensorState <- modSim::mongoUnnest(mongoData = sensorState,
                                                     unnestCols = "status")
    
    sensorDescription <- dplyr::distinct(.data = sensorState,
                                         sensorId,
                                         acquireSensorType,
                                         magnification)
    
    entityIdToName <- dplyr::distinct(.data = sensorState,
                                      entityId,
                                      source)
    
    sensorToEntity <- dplyr::distinct(.data = sensorState,
                                      sensorId,
                                      entityId)
  
    return(list("SensorDescription" = sensorDescription,
                "EntityIdToName" = entityIdToName,
                "SensorToEntityId" = sensorToEntity,
                "UnnestedSensorState" = sensorState))
    
} # close mapSensorsAndEntities function

```  


```{r}
mapSensorsAndEntities(mongoUri = mongoUri,
                      mongoDb = mongoDb,
                      mongoCollection = sensorIDNameCollection,
                      mongoFields = sensorIDNameFields,
                      mongoQuery = sensorIDNameQuery)

```
