---
title: "Step 3: Query, Plot, and Analyze Simulation Data from PostgreSQL"
author: "Neil Kester"
date: "4/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE)
```

# Purpose  

This step interacts with the data only through the two materialized views created in PostgreSQL. They are named: `los_sensor_target_pairs_materialized` for the line of sight (LOS) data and `acq_sensor_target_pairs_materialized` for the sensor acquisition data.  

# Low Functions  

## Query Data: `queryData()`  

This function is used to pull in data from both materialized views based on the same common filter parameters.  

Specifically, this is used to produce a list of two tibbles with data pertaining to a target force (`BLUE FORCE`or `REDFORCE`), a sensor force (`BLUE FORCE` or `REDFORCE`), and a design point. If multiple design points ore force combinations are required, execute the function multiple times and combine the results.  

```{r low_queryData}

#' Query ModSim Materialized Views
#' 
#' This function queries the materialized views created in Step 1 and filled in
#'  Step 2. 
#'
#' @author Neil Kester, \email{nkester1@@jhu.edu}
#'
#' @param connParamList A five element named list containing the following elements:
#'  "pgHost", "pgPort", "pgUser", "pgPass", and "pgDb".
#' @param sensorForce This is either "BLUEFORCE" or "REDFORCE".
#' @param targetForce This is either "BLUEFORCE" or "REDFORCE".
#' @param designPoint This is a string name describing the designPoint as stored
#'  in the PostgreSQL datanase.
#'
#' @return This returns a named list of two elements, the results from the LOS
#'  and the ACQ Materialized View queries.
#'  
#' @importFrom DBI dbConnect dbGetQuery dbDisconnect  
#'
#' @export queryData
#'
#' @note Location: ./R/fct_step3_low_queryData.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
queryData <- function(pgConnParam,
                      sensorForce,
                      targetForce,
                      designPoint){
  
  pgConn <- DBI::dbConnect(drv = RPostgreSQL::PostgreSQL(),
                           host = pgConnParam[["pgHost"]],
                           port = pgConnParam[["pgPort"]],
                           user = pgConnParam[["pgUser"]],
                           password = pgConnParam[["pgPass"]],
                           dbname = pgConnParam[["pgDb"]])
  
  query_losMatViewData <- sprintf("
      SELECT \"time_s\", \"sensorShortName\", \"iteration\", \"designPoint\", \"hasLOS\",\"targetShortName\"
      FROM los_sensor_target_pairs_materialized
      WHERE \"sensorForce\" = '%s' AND \"targetForce\" = '%s' AND \"designPoint\" = '%s'
      ",
      sensorForce,
      targetForce,
      designPoint)
  
  query_acqMatViewData <- sprintf("
      SELECT \"time_s\", \"sensorShortName\", \"iteration\", \"designPoint\", \"hasAcq\",\"targetShortName\"
      FROM acq_sensor_target_pairs_materialized
      WHERE \"sensorForce\" = '%s' AND \"targetForce\" = '%s' AND \"designPoint\" = '%s'
      ",
      sensorForce,
      targetForce,
      designPoint)
  
  losMatViewData <- DBI::dbGetQuery(conn = pgConn,
                                    statement = query_losMatViewData)
  
  acqMatViewData <- DBI::dbGetQuery(conn = pgConn,
                                    statement = query_acqMatViewData)
  
  DBI::dbDisconnect(conn = pgConn)
  
  rm(pgConn)
  
  return(list("losMatViewData" = losMatViewData,
              "acqMatViewData" = acqMatViewData))
  
} # close low_queryData
```  

## Graph Data Prep: `graphDataPrep()`  


```{r low_graphDataPrep}
#' Prepare the Queried Data for Analysis
#'
#' This takes the results from `low_queryData` and returns expanded data for each
#'  time step both at the iteration level and also aggregated to the designPoint
#'  level.
#'
#' @author Neil Kester, \email{nkester1@@jhu.edu}
#'
#' @param losMatViewData A tibble resulting from the `low_queryData` function.
#' @param acqMatViewData A tibble resulting from the `low_queryData` function.
#' @param sensor A single character string for the sensor you want to structure
#'  data for. For multiple sensors, execute this function multiple times.
#'
#' @return A four element named list of raw (by iteration) and aggregated (mean)
#'  data for line of sight and acquisition data.
#'
#' @importFrom dplyr mutate distinct_all filter group_by summarise ungroup
#'  select n left_join
#' @importFrom tidyr unnest fill replace_na
#'
#' @export graphDataPrep
#'
#' @note Location: ./R/fct_step3_low_graphDataPrep.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
graphDataPrep <- function(losMatViewData,
                          acqMatViewData,
                          sensor){
  
  { # LOS Data Prep
    
    los <- losMatViewData %>%
      dplyr::mutate(time_s = as.numeric(time_s)) %>%
      dplyr::mutate(time_s = round(x = time_s,digits = 0)) %>%
      dplyr::distinct_all() %>%
      dplyr::filter(sensorShortName %in% sensor) %>%
      dplyr::group_by(time_s,
                      sensorShortName,
                      iteration,
                      designPoint) %>%
      dplyr::summarise(count = sum(hasLOS),
                       .groups = "keep") %>%
      dplyr::ungroup() %>%
      dplyr::select(-sensorShortName)
    
    los2 <- losMatViewData %>%
      dplyr::group_by(designPoint,
                      iteration) %>%
      dplyr::mutate(time_s = as.numeric(x = time_s)) %>%
      dplyr::mutate(time_s = round(x = time_s,
                                   digits = 0)) %>%
      dplyr::summarise(maxTime = max(time_s),
                       .groups = "keep") %>%
      dplyr::ungroup() %>%
      dplyr::mutate(time_s = list(0:maxTime)) %>%
      dplyr::select(-maxTime) %>%
      tidyr::unnest(time_s) %>%
      dplyr::select(time_s,
                    designPoint,
                    iteration) %>%
      dplyr::left_join(x = .,
                       y = los,
                       by = c("time_s",
                              "designPoint",
                              "iteration")) %>%
      tidyr::fill(data = .,
                  count,
                  .direction = "down") %>%
      tidyr::replace_na(list(count = 0)) %>%
      dplyr::mutate(sensorShortName = sensor,
                    type = "LOS")
    
    los3 <- los2 %>%
      dplyr::group_by(time_s,designPoint,sensorShortName) %>%
      dplyr::summarise(count_mean = mean(count),
                       count_var = var(count),
                       count_sd = sd(count),
                       count_se = count_sd/sqrt(dplyr::n()),
                       type = "LOS",
                       .groups = "keep") %>%
      dplyr::ungroup()
    
  } # close LOS Data Prep
  
  { # ACQ Data Prep
    
    acq <- acqMatViewData %>%
      dplyr::mutate(time_s = as.numeric(time_s)) %>%
      dplyr::mutate(time_s = round(x = time_s,
                                   digits = 0)) %>%
      dplyr::distinct_all() %>%
      dplyr::filter(sensorShortName %in% sensor) %>%
      dplyr::group_by(time_s,
                      sensorShortName,
                      iteration,
                      designPoint) %>%
      dplyr::summarise(count = sum(hasAcq),
                       .groups = "keep") %>%
      dplyr::ungroup() %>%
      dplyr::select(-sensorShortName)
    
    acq2 <- acqMatViewData %>%
      dplyr::group_by(designPoint,iteration) %>%
      dplyr::mutate(time_s = as.numeric(x = time_s)) %>%
      dplyr::mutate(time_s = round(x = time_s,
                                   digits = 0)) %>%
      dplyr::summarise(maxTime = max(time_s),
                       .groups = "keep") %>%
      dplyr::ungroup() %>%
      dplyr::mutate(time_s = list(0:maxTime)) %>%
      dplyr::select(-maxTime) %>%
      tidyr::unnest(time_s) %>%
      dplyr::select(time_s,
                    designPoint,
                    iteration) %>%
      dplyr::left_join(x = .,
                       y = acq,
                       by = c("time_s",
                              "designPoint",
                              "iteration")) %>%
      tidyr::fill(data = .,
                  count,
                  .direction = "down") %>%
      tidyr::replace_na(list(count = 0)) %>%
      dplyr::mutate(sensorShortName = sensor,
                    type = "ACQ")
    
    acq3 <- acq2 %>%
      dplyr::group_by(time_s,designPoint,sensorShortName) %>%
      dplyr::summarise(count_mean = mean(count),
                       count_var = var(count),
                       count_sd = sd(count),
                       count_se = count_sd/sqrt(dplyr::n()),
                       type = "ACQ",
                       .groups = "keep") %>%
      dplyr::ungroup()
    
  } # close ACQ Data Prep
  
  return(list("LOSbyIteration" = los2,
              "LOSmeanByDesignPoint" = los3,
              "ACQbyIteration" = acq2,
              "ACQmeanByDesignPoint" = acq3))
  
} # close graphData Prep function

```

## Target Column Graph Data: `targetColumnGraphData()`  

This data is aggregated at the target level in order to see which targets the sensor entity is viewing.

```{r}
#' Target-Sensor Entity Data
#'
#' This function prepares the LOS and ACQ data at the target level by time step
#'  rather than the design point level. This allows us to understand which targets
#'  the chosen sensor has line of sight with and which it is able to acquire.
#'
#' @author Neil Kester, \email{nkester1@@jhu.edu}
#'
#' @param losMatViewData A tibble resulting from the `low_queryData` function.
#' @param acqMatViewData A tibble resulting from the `low_queryData` function.
#' @param sensor A single character string for the sensor you want to structure
#'  data for. For multiple sensors, execute this function multiple times.
#'
#' @return This function returns a single tibble of time, sensor name, iteration,
#'  design point, target name, and type (LOS or ACQ).
#'
#' @importFrom dplyr mutate distinct_all filter group_by summarise n ungroup
#'  bind_rows
#' @importFrom tidyr replace_na
#'
#' @note Location: ./R/fct_step3_low_targetColumnGraphData.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
targetColumnGraphData <- function(losMatViewData,
                                  acqMatViewData,
                                  sensor){

  { # LOS Data Prep

    los <- losMatViewData %>%
      dplyr::mutate(time_s = as.numeric(time_s)) %>%
      dplyr::mutate(time_s = round(x = time_s,
                                   digits = 0)) %>%
      dplyr::distinct_all() %>%
      dplyr::filter(sensorShortName %in% sensor) %>%
      dplyr::group_by(time_s,
                      sensorShortName,
                      iteration,
                      designPoint,
                      targetShortName) %>%
      dplyr::summarise(count = sum(hasLOS),
                       .groups = "keep") %>%
      dplyr::ungroup() %>%
      dplyr::group_by(time_s,
                      sensorShortName,
                      designPoint,
                      targetShortName) %>%
      tidyr::replace_na(list(count = 0)) %>%
      dplyr::summarise(count_mean = mean(count),
                       count_var = var(count),
                       count_sd = sd(count),
                       count_se = count_sd/sqrt(dplyr::n()),
                       type = "LOS",
                       .groups = "keep") %>%
      dplyr::ungroup()

  } # close LOS Data Prep

  { # ACQ Data Prep

    acq <- acqMatViewData %>%
      dplyr::mutate(time_s = as.numeric(time_s)) %>%
      dplyr::mutate(time_s = round(x = time_s,
                                   digits = 0)) %>%
      dplyr::distinct_all() %>%
      dplyr::filter(sensorShortName %in% sensor) %>%
      dplyr::group_by(time_s,
                      sensorShortName,
                      iteration,
                      designPoint,
                      targetShortName) %>%
      dplyr::summarise(count = sum(hasAcq),
                       .groups = "keep") %>%
      dplyr::ungroup() %>%
      dplyr::group_by(time_s,
                      sensorShortName,
                      designPoint,
                      targetShortName) %>%
      tidyr::replace_na(list(count = 0)) %>%
      dplyr::summarise(count_mean = mean(count),
                       count_var = var(count),
                       count_sd = sd(count),
                       count_se = count_sd/sqrt(dplyr::n()),
                       type = "ACQ",
                       .groups = "keep") %>%
      dplyr::ungroup()

  } # close ACQ Data Prep

  histData <- dplyr::bind_rows(los,acq)

  return(histData)

} # close targetColumnGraphData function

```

## Calculate the mean difference by time step between LOS and ACQ  

```{r}
#' Find the mean difference between the # of LOS and ACQ per timestep
#'
#' @param iterationData from modSim::Step3_multiDesingPointAndSensorDataPrep
#'
#' @export Step3_meanDiffByDesignPointAndTime
#'
#' @importFrom dplyr select mutate group_by summaris n ungroup
#' @importFrom tidyr pivot_wider
#'
#' @note Location: ./R/fct_step3_low_targetColumnGraphData.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
Step3_meanDiffByDesignPointAndTime <- function(iterationData){
  
  meanDiffByDesignPointAndTime <- graphData$byIteration %>%
  dplyr::select(time_s,designPoint,iteration,sensorShortName,count,type) %>%
  tidyr::pivot_wider(names_from = type,values_from = count) %>%
  dplyr::mutate(diff = LOS - ACQ) %>%
  dplyr::group_by(time_s,designPoint,sensorShortName) %>%
  dplyr::summarise(diff_mean = mean(diff),
                   diff_sd = sd(diff),
                   diff_var = var(diff),
                   diff_se = diff_sd/sqrt(dplyr::n()),
                   .groups = "keep") %>%
  dplyr::ungroup()
  
  return(meanDiffByDesignPointAndTime)
  
}
```

## Graph mean difference data  

```{r}
#' Graph the mean difference between LOS and ACQ
#'
#' @param meanIterationData Means found over iterations
#'
#' @return
#' @export Step3_graphMeanIterations
#'
#' @importFrom ggplot2 ggplot geom_point aes theme_minimal labs facet_grid
#'
#' @note Location: ./R/fct_step3_low_graphMeanIterations.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
Step3_graphMeanIterations <- function(meanIterationData){
  
  p <- ggplot2::ggplot(meanDiffByDesignPointAndTime) +
    ggplot2::geom_point(mapping = ggplot2::aes(x = time_s,
                                               y = diff_mean)) +
    ggplot2::theme_minimal() +
    ggplot2::labs(x = "time (s)",
                  y = "Mean Difference Between LOS and ACQ",
                  title = "Difference between a sensor's LOS and ACQ records by time step") +
    ggplot2::facet_grid(sensorShortName ~ designPoint)
  
  return(p)
  
} # close Step3_graphMeanIterations function
```

## Produce box plot of difference data  

```{r}
#' Calculate and Produce Boxplot of data across iterations.
#'
#' @param iterationData raw data without summarization
#'
#' @return plot and data
#' @export Step3_boxPlotOfDifferences
#'
#' @importFrom dplyr select mutate
#' @importFrom tidyr pivot_wider
#' @importFrom ggplot2 ggplot geom_boxplot aes theme_minimal theme element_text
#'
#' @note Location: ./R/fct_step3_low_boxPlotOfDifferences.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
Step3_boxPlotOfDifferences <- function(iterationData){
  
  DiffByDesignPoint <- iterationData %>%
  dplyr::select(time_s,designPoint,iteration,sensorShortName,count,type) %>%
  tidyr::pivot_wider(names_from = type,values_from = count) %>%
  dplyr::mutate(diff = LOS - ACQ) 

  p <- ggplot2::ggplot(DiffByDesignPoint) +
    ggplot2::geom_boxplot(mapping = ggplot2::aes(x = designPoint,y = diff)) +
    ggplot2::theme_minimal() +
    ggplot2::theme(strip.text.y = ggplot2::element_text(angle = 0))
  
  return(list(DiffByDesignPoint,
              p))
  
}
```


# Mid Functions




# High Functions

## Prepare Data for Multiple Design Points and Sensors: `Step3_multiDesingPointAndSensorDataPrep()`  

This high level function is used to query and prepare data in the two PostgreSQL Materialized views for analysis and graphing. 

```{r Step3_multiDesingPointAndSensorDataPrep}
#' Query and Prepare Data for Multiple Design Points and Sensors
#'
#' This function executes and integrates the two Step 3 low functions across a
#'  number of designPoints and sensor entities.
#'
#' @author Neil Kester, \email{nkester1@@jhu.edu}
#'
#' @param connParamList A five element named list containing the following elements:
#'  "pgHost", "pgPort", "pgUser", "pgPass", and "pgDb".
#' @param sensorForce This is either "BLUEFORCE" or "REDFORCE".
#' @param targetForce This is either "BLUEFORCE" or "REDFORCE".
#' @param designPoints This is a character vector of names describing designPoints
#'  as stored in the PostgreSQL datanase.
#' @param sensors This is a character vector of sensor entity names you want to
#'  structure data for.
#'
#' @return This returns a two element named list of consolidated data at the iteration
#'  and designPoint level. DesignPoint level data is aggregated across the iterations
#'  executed for each designPoint. Metrics calculated for that aggregation include
#'  the mean, variance, standard deviation, and standard error.
#'
#' @export Step3_multiDesingPointAndSensorDataPrep
#'
#' @importFrom tibble tibble
#' @importFrom dplyr bind_rows
#' @importFrom tidyr drop_na
#'
#' @note Location: ./R/fct_step3_high_multiDesignPointAndSensorDataPrep.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
Step3_multiDesingPointAndSensorDataPrep <- function(pgConnParam,
                                                    sensorForce,
                                                    targetForce,
                                                    designPoint,
                                                    sensors){

  { # set up

    consolidateGraphDataIteration <- tibble::tibble(time_s = NA,
                                                    designPoint = NA,
                                                    iteration = NA,
                                                    count = NA,
                                                    sensorShortName = NA)

    consolidateGraphDataMean <- tibble::tibble(time_s = NA,
                                               designPoint = NA,
                                               sensorShortName = NA,
                                               count_mean = NA,
                                               count_var = NA,
                                               count_sd = NA,
                                               count_se = NA)

    consolidateGraphDataTargetColumn <- tibble::tibble(time_s = NA,
                                                       sensorShortName = NA,
                                                       designPoint = NA,
                                                       targetShortName = NA,
                                                       count_mean = NA,
                                                       count_var = NA,
                                                       count_sd = NA,
                                                       count_se = NA,
                                                       type = NA)

  } # close set up

  for(designPoint in designPoints){

    message(paste0("\nWorking on ",
                   designPoint,
                   " designPoint.\n"))

    { # Query

      designPointData <- queryData(pgConnParam = pgConnParam,
                                   sensorForce = sensorForce,
                                   targetForce = targetForce,
                                   designPoint = designPoint)

    } # close Query

    for(sensor in sensors){

      message(paste0("\nWorking on ",
                     sensor,
                     " sensor in ",
                     designPoint,
                     " designPoint.\n"))

      temp <- graphDataPrep(losMatViewData = designPointData$losMatViewData,
                            acqMatViewData = designPointData$acqMatViewData,
                            sensor = sensor)

      hist <- targetColumnGraphData(losMatViewData = designPointData$losMatViewData,
                                    acqMatViewData = designPointData$acqMatViewData,
                                    sensor = sensor)

      consolidateGraphDataIteration <- dplyr::bind_rows(temp$LOSbyIteration,
                                                        temp$ACQbyIteration,
                                                        consolidateGraphDataIteration)

      consolidateGraphDataMean <- dplyr::bind_rows(temp$LOSmeanByDesignPoint,
                                                   temp$ACQmeanByDesignPoint,
                                                   consolidateGraphDataMean)

      consolidateGraphDataTargetColumn <- dplyr::bind_rows(consolidateGraphDataTargetColumn,
                                                           hist)

      rm(temp,hist)

    } # close sensors loop

    rm(designPointData)

  } # close designPoints loop

  consolidateGraphDataIteration <- tidyr::drop_na(consolidateGraphDataIteration)

  consolidateGraphDataMean <- tidyr::drop_na(consolidateGraphDataMean)

  consolidateGraphDataTargetColumn <- tidyr::drop_na(consolidateGraphDataTargetColumn)

  return(list("byIteration" = consolidateGraphDataIteration,
              "byDesignPoint" = consolidateGraphDataMean,
              "byTarget" = consolidateGraphDataTargetColumn))

} # close Step3_multiDesingPointAndSensorDataPrep function


```

## Graph Mean 

```{r}
#' Graph the Mean Data
#'
#' Return a consistent formatted graph of the data.
#'
#' @author Neil Kester, \email{nkester1@@jhu.edu}
#'
#' @param graphData This is the mean data resulting from `multiDesignPointAndSensorDataPrep`
#'  function
#' @param losColor A color string
#' @param acqColor A color string
#' @param errorbars Boolean
#'
#' @return A ggplot2 plot
#'
#' @export Step3_graphMean
#'
#' @importFrom ggplot2 ggplot geom_point aes scale_color_manual theme_minimal theme
#'  element_text labs facet_grid geom_errorbar
#'
#' @note Location: ./R/fct_step3_high_graphMean.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
Step3_graphMean <- function(graphData,
                           losColor = "blue",
                           acqColor = "black",
                           errorbars=TRUE){
  
  p <- ggplot2::ggplot(data = graphData) +
    ggplot2::geom_point(mapping = ggplot2::aes(x = time_s,
                                               y = count_mean,
                                               color = type)) +
    ggplot2::scale_color_manual(values = c(losColor,
                                           acqColor),
                                name = "Type") +
    ggplot2::theme_minimal() +
    ggplot2::theme(strip.text.y = ggplot2::element_text(angle = 0)) +
    ggplot2::labs(x = "time (s)",
                  y = "Mean Target Count",
                  title = "Line of Sight and Positive Sensor Acquisitions Over Time",
                  subtitle = "Error bars show mean +- standard error") +
    ggplot2::facet_grid(sensorShortName ~ designPoint)
  
  if(errorbars){
    
    p <- p +
      ggplot2::geom_errorbar(mapping = ggplot2::aes(x = time_s,
                                                    ymax = count_mean + count_se,
                                                    ymin = count_mean - count_se,
                                                    color = type),
                             alpha = 0.25)
    
  } # close if errorbars
  
  return(p)
  
} # Step3_graphMean function
```

## Produce Column Plot of Multiple DesignPoints for a Single Sensor  


```{r}

#' Graph the Sensor - Target Column Chart, Faceted by Design Point
#'
#' This function accepts parameters, fetches data, transforms it, and produces a
#'  graph that shows the number of target entities a sensor entity has line of
#'  sight with and has acquired. This is further broken down by color that
#'  corresponds to the target's name.
#'
#' @param sensorForce This is either "BLUEFORCE" or "REDFORCE".
#' @param targetForce This is either "BLUEFORCE" or "REDFORCE".
#' @param designPoints This is a character vector of names describing designPoints
#'  as stored in the PostgreSQL datanase.
#' @param connParamList A five element named list containing the following elements:
#'  "pgHost", "pgPort", "pgUser", "pgPass", and "pgDb".
#' @param sensors This is a character vector of sensor entity names you want to
#'  structure data for.
#'
#' @return This returns a list of two elements, the data and the plot it made.
#' @export graphTargetColumnByDesignPoint
#'
#' @importFrom tibble tibble
#' @importFrom dplyr bind_rows
#' @importFrom ggplot2 ggplot geom_col aes facet_grid theme_minimal theme element_text
#'
#' @note Location: ./R/fct_step3_high_graphTargetColumnByDesignPoint.R
#' @note RMarkdown location: ./inst/step3_plotting/Step3_plotting.Rmd
graphTargetColumnByDesignPoint <- function(consolidateGraphDataTargetColumn){


  { # Produce the Plot

    p <-ggplot2::ggplot(consolidateGraphDataTargetColumn) +
      ggplot2::geom_col(mapping = ggplot2::aes(x = time_s,
                                               y = count_mean,
                                               fill = targetShortName)) +
      #ggplot2::geom_errorbar(mapping = ggplot2::aes(x = time_s,ymax = count_mean + count_se,ymin = count_mean - count_se,color = targetShortName)) +
      ggplot2::facet_grid(type ~ designPoint) +
      ggplot2::theme_minimal() +
      ggplot2::theme(title = ggplot2::element_text("LOS and ACQ broken out by DesignPoint and Target"))

  } # close Produce the Plot

  return(p)

} # close graphTargetColumnByDesign function

```

```{r commonParameters}
library(magrittr)
#> These source files read in the mongoURI and mongoDb elements and the PostgreSQL connection objects.

source("./connectionObjects/pgConnectionObj.R")
source("./connectionObjects/mongoConnectionObj.R")

#> Add to the pgConnParam the database name 

pgConnParam[["pgDb"]] <- "modSim"


designPoints <- "WASP1_high_high_20210426"
designPoint <- "WASP1_low_low_20210426"

designPoints <- c("WASP1_high_high_20210426","WASP1_low_low_20210426")

sensorForce <- "BLUEFORCE"
targetForce <- "REDFORCE"

sensors <- c("EPBV 90 1","EPBV 90 2","WASP 1")

losColor <- "blue"

acqColor <- "black"

```

```{r}

graphData <- high_multiDesingPointAndSensorDataPrep(pgConnParam = pgConnParam,
                                                    sensorForce = sensorForce,
                                                    targetForce = targetForce,
                                                    designPoints = designPoints,
                                                    sensors = sensors)

```
```{r}

```







```{r}

high_graphMean(graphData = graphData$byDesignPoint,
               losColor = losColor,
               acqColor = acqColor,
               errorbars = FALSE)

```


